\documentclass[a4paper, oneside, final]{scrartcl}

\usepackage[utf8x]{inputenc}
\usepackage[brazil]{babel}
\usepackage{amssymb}

\usepackage{soul}
\usepackage{scrpage2}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{tabularx}
\usepackage{textcomp}

\usepackage[hmargin=2cm,vmargin=2.5cm,noheadfoot]{geometry}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\pagestyle{scrheadings}
\renewcommand{\headfont}{\normalfont\rmfamily\scshape}

% add the symbols for email and phone contact data
\cofoot{
%\so{Av. Xxxxxxxxx xx Xxxxx, YYYY - São Paulo, SP} \\
%\so{ {\Large\Letter} 
suelengcarvalho@gmail.com \ 
%{\Large\Telefon} 
+55 (11) 9336-7069
%} 
}

\begin{document}

\begin{center}
\textsc{\Huge{Suelen Goularte Carvalho}}\\
\ \\
%\textsc{\huge{\so{Suelen Goularte Carvalho}}}\\ \ \\
%{\small \tt Pretenção Salarial: R\$ 10.000,00 CLT Full}

\section{Purpose}
	PROJECT LEADER / SCRUM MASTER / SENIOR DEVELOPMENT ANALYST 

\section{Personal Information}

\begin{tabularx}{.97\linewidth}{p{3.0cm}p{4.0cm}p{3.0cm}X}
Phone:           & +55 (11) 9336-7069 & Email:        & suelengcarvalho@gmail.com \\
Date of Birth: & 26/02/1987     & Marital Status: & Single\\
%\                   & \              & Linkedin:     & http://www.linkedin.com/in/suelengc 
\end{tabularx}

\section{Resume}

\begin{tabularx}{0.97\linewidth}{X}
	7 years of experience in analysis and development of web systems, two years of teaching in the area of ​​software development. \\ \ \\

	Enthusiast agile, responsive, highly entrepreneurial, with provision for challenges and innovative projects.
\end{tabularx}

\section{Academic Background}

\begin{tabularx}{0.97\linewidth}{p{2cm}X}
2010$-$2012 & Expert degree in Strategic Management of Projects\\
            & Instituto Tecnológico de Aeronáutica, ITA\\
            & \\

2005$-$2008 & Bachelor degree in Analysis and Systems Development\\
            & Faculdade de Tecnologia Diamantes, FATED\\
            & \\

2003$-$2003 & Technical degree in Data Processing\\
            & Escola Profissional Nossa Senhora de Fátima, SENAI\\

\end{tabularx}

\section{Complementary Training}

\begin{tabularx}{0.97\linewidth}{p{2cm}X}

2010       & Academy Java (128h)\\
           & Globalcode\\ 
           & \\

2010       & Linear Algebra (120h) \\
           & Universidade de São Paulo, USP\\
           & \\

2009       & Topics Programming (60h)\\
           & Universidade de São Paulo, USP\\
           & \\

2008       & Academy .Net (VB, ASP, C\# e ADO) (144h)\\
           & Ká Solutions\\
           & \\

2004       & English (240h)\\
           & Escola Profissional Nossa Senhora de Fátima, SENAI

\end{tabularx}

%\section{Certificações}
%
%\begin{tabularx}{0.97\linewidth}{p{2cm}X}
%2011        & SCJP --- Sun Certified Java Programmer\\ \\
%\end{tabularx}

\section{Professional Experience}

\begin{tabularx}{0.97\linewidth}{p{2cm}X}

Company     & Liberty Seguros $-$ Emphasys Consulting \\
Function    & Web Project Leader\\
Period      & 04/2011 $-$ Current \\
Activities  & Acting in leading projects that use web technologies VB.Net, ASP.Net (Framework 3.5, 2.0 and 1.1 with Visual Studio 2010, 2008, 2005 and 2003) and SharePoint 10. Conducting a survey of the scope and requirements, development planning, alignment of expectations, communication management and mains project. Acting directly on the analysis and development of web systems. \\
            & \ \\

Company     & Serasa Experian\\
Function    & Systems Analyst\\
Period      & 10/2010 $-$ 04/2011\\
Activities  & Implementation of agile management team in corrective maintenance. Java Web Development (using Eclipse, Websphere and Harvest). Development VB.Net and C \#. Net (framework 1.1, 2.0, 3.5 and 4.0 with Visual Studio 2010, 2008, 2005 and 2003). Implementation of metrics to improve the quality of software development. \\
            & \ \\

Company     & Liberty Seguros $-$ Stefanini Consulting \\
Function    & Senior Systems Analyst \\
Period      & 11/06 $-$ 10/2010 \\
Activities  & Development and maintenance of systems and webservices in VB.Net, ASP.NET and Javascript using multiple layers architecture and SOA. The main activities included web development, development planning and schedules, negotiating deadlines, tracking approvals, user support and delegation of activities to other analysts. \\
            & \ \\

Company     & Intersaúde $-$ Emphasys Consulting \\
Function    & Programmer Analyst Full \\
Period      & 09/2006 $-$ 11/2006  \\
Activities  & Participação em projetos de desenvolvimento utilizando Visual Basic e Delphi. \\ 
            & \ \\

Company     & Signa Logística do E-Business \\
Function    & Full Programmer \\
Period      & 04/2006 $-$ 09/2006  \\
Activities  & Development of systems using multiple technologies $ - $ ASP, VBScript, Visual Basic, HTML, XML, CSS and JavaScript. Development and maintenance of stored procedures, triggers in Oracle systems and Microsoft SQL Server. \\ 
\end{tabularx}

\section{Academic Experience}

\begin{tabularx}{0.97\linewidth}{p{2cm}X}

Company     & Colégio SAA\\
Function    & Professor \\
Period      & 02/2012 $-$ Atual \\
Activities  & Professor of the disciplines of professional course in Computer Programming Concepts and Implementation of Systems with Java. \\ 
            & \ \\

\end{tabularx}
\begin{tabularx}{0.97\linewidth}{p{2cm}X}

Company     & Universidade Bandeirantes, UNIBAN \\
Function    & Professor \\
Period      & 04/2009 $-$ 08/2009 \\
Activities  & Professor of undergraduate course Web Development. \\ 
            & \ \\

\end{tabularx}
\begin{tabularx}{0.97\linewidth}{p{2cm}X}

Company     & Faculdade de Tecnologia Diamantes, FATED \\
Function    & Professor  \\
Period      & 06/2008 $-$ 06/2009 \\
Activities  & Professor of graduate courses in Web Development and Practice of Object Orientation with Java. \\ 
            & \ \\

\end{tabularx}
\begin{tabularx}{0.97\linewidth}{p{2cm}X}

Company     & Faculdade Paulista de Artes, FPA \\
Function    & Professor \\
Period      & 05/2007 $-$ 07/2007 \\
Activities  & Professor of discipline extracurricular travel Web Development with PHP. \\ 

\end{tabularx}

\section{Languages}

\begin{tabularx}{0.97\linewidth}{p{2cm}X}
English      & Advanced\\
\end{tabularx}

\section{knowledge}

\begin{tabularx}{0.97\linewidth}{p{3.0cm}X}
Agile Practices: & Scrum, Lean, XP and TDD\\
Languages:       & C\#.Net, ASP.Net, VB.Net, VBScript, PHP, C/C++, Delphi, Java and JSP \\
Severs:          & Websphere, IIS, Tomcat and Apache \\
Frameworks:      & .Net, Spring, Struts, Hibernate, CakePHP and JQuery \\
Technologies:    & HTML, CSS, XML, XSL, DTD, Javascript, Json, Ajax and Transact SQL \\
Applications:    & Photoshop, Ilustrator and Dreamweaver \\
Databases:       & MySQL, Oracle and Microsoft SQL Server \\
Tools:           & Visual Studio, Eclipse, Netbeans, Source Safe, Team System and Harvest \\
\end{tabularx}

%\section{Publications}
%\section{Interests}

\end{center}

\end{document}
